### 2013-11-12 PositionPaper/introduction.tex
no message

Current data management approaches on the cloud tend to use NoSQL stores for managing huge heterogeneous data collections (graph, key-value, tables, relational): polyglot approaches. 
Yet, having such heterogeneous schema-less data stores, calls for efficient methods for integrating (correlating, associating, filtering) heterogeneous data collections taking into consideration their ``structural'' characteristics (due to the different data models) but also their quality of service, e.g., trust, freshness, provenance, partial or total consistency. 
Existing data integration techniques based on mappings, views management, ontologies have to be revisited in order to integrate data that are weakly curated and described through metadata or schemas.

{\color{green} 
Furthermore, security aspects are crucial in integrating big data. Indeed, the integration task must guarantee the integrity and privacy of data, the willingness of the clouds to well contribute to the security process through acceptable runtime environment conditions, and the adequacy of the proposed security levels to the services behind the integration operation.
}

@@

The objectives of our work are to propose an SLA guided continuous data provision and integration system that will be exported as a DaaS by a cloud provider. 
Therefore we propose strategies for computing integrated SLA’s according to agreed SLA’s proposed by services and optimized and adaptable query rewriting and bi data sets integration according to user preferences. 
Given the computational cost of a query evaluation, our approach uses automatic learning techniques for generating knowledge out of every task and reducing its economic cost.

@@

>>>>

Current data management approaches on the cloud tend to use NoSQL stores for managing huge heterogeneous data collections (graph, key-value, tables, relational). 
Yet, having such heterogeneous schema-less data stores, calls for efficient methods for integrating (correlating, associating, filtering) heterogeneous data collections taking into consideration their ``structural'' characteristics (due to the different data models) but also their quality of service, e.g., trust, freshness, provenance, partial or total consistency. 
Existing data integration techniques based on mappings, views management, ontologies have to be revisited in order to integrate data that are weakly curated and described through metadata or schemas.

%{\color{green} 
%Furthermore, security aspects are crucial in integrating big data. Indeed, the integration task must guarantee the integrity and privacy of data, the willingness of the clouds to  contribute to the security process through acceptable runtime environment conditions, and the adequacy of the proposed security levels to the services behind the integration operation.
%}

@@

The objectives of our work are to propose an SLA guided continuous data provision and integration system exported as a DaaS by a cloud provider. 
Therefore we propose strategies for computing integrated SLA’s according to agreed SLA’s proposed by services and optimized and adaptable query rewriting for integrating data sets  according to user profiles. 
%Given the computational cost of a query evaluation and a user profile, our approach uses automatic learning techniques for generating knowledge out of every task and reducing query evaluation economic cost.

@@

Accordingly, the remainder of this paper is organized as follows. Section \ref{sec:relWork} presents related works that address SLA modelling, integration and SLA guided data management processes. Section \ref{sec:slaDataInteg} gives an overview of our approach for integrating data sets provided by services (i.e., DaaS) by concilating SLA's provided by services and user's profiles expressing QoS preferences about the data they want to consume and the conditions in which they must be processed and delivered. Section \ref{sec:incremental} introduces on demand and incremental data integration strategies. Section \ref{sec:useCase}presents a use case for illustrating the interest and use of our approach. Finally \ref{sec:conclusions} concludes the papers and discusses future work.
